A molecular taxonomy of tumors independent of tissue-of-origin

### 2020-07-21 text/discussion.Rmd
add pcawg annotation-aware annotation reference to discussion

We find that most tumors segregate into one of 12 biologically distinct
clusters, regardless of the cancer type (**figure 1h** and **supplementary
figure S1**). Some cancer types ( _e.g._ pancreatic adenocarcinomas in the RAS
arm clusters 9 and 10, and breast cancers being excluded from the same cluster,
see **supplementary figure S1**) are unevenly distributed, though we could not
identify cancer type that was exclusive to a single tumor class. Somewhat
surprisingly to us, this finding extends to histological subtypes of breast,
head and neck cancers, leukemias, _etc._ (see **Figure 1i** and **Supplemental
Figure S2**). Indeed, it would be surprising if we did not observe bias for some
cancers, as it has long been known that certain treatment regimens are likely to
work for a significant fraction of patients of a given cancer type. Nonetheless,
the basis for some tumors being treatment-refractory in spite of clinical
indications remains elusive. Our analysis suggests the possibility of
identifying more informative molecular, histological or cellular subtypes and
could form a basis for future separation of patients into different precision
treatment regimens.

>>>>

We find that most tumors segregate into one of twelve biologically distinct
clusters, regardless of the cancer type (**figure 1h** and **supplementary
figure S1**). Some cancer types ( _e.g._ pancreatic adenocarcinomas in the RAS
arm clusters 9 and 10, and breast cancers being excluded from the same cluster,
see **supplementary figure S1**) are unevenly distributed, though we could not
identify cancer type that was exclusive to a single tumor class. Somewhat
surprisingly to us, this finding extends to histological subtypes of breast,
head and neck cancers, leukemias, _etc._ (see **Figure 1i** and **Supplemental
Figure S2**). Indeed, it would be surprising if we did not observe bias for some
cancers, as it has long been known that certain treatment regimens are likely to
work for a significant fraction of patients of a given cancer type. Nonetheless,
the basis for some tumors being treatment-refractory in spite of clinical
indications remains elusive. Our analysis suggests the possibility of
identifying more informative molecular, histological or cellular subtypes and
could form a basis for future separation of patients into different precision
treatment regimens.
